Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
New FDS Images Corner

>>>>

\begin{figure}[p]
	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner1}
	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner2}
	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner3} \\

	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner4}
	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner5} 
	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner6} \\

	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner7}
	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner8}
	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner9} \\

	\caption[Image sequence of an FDS/Smokeview simulation of the natural gas burner positioned in a corner.]{Image sequence of an FDS/Smokeview simulation of the natural gas burner positioned in a corner. The time interval between images is 0.3 of second.}
	\label{GBNG34Sequence}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=2.5in]{../Figures/10}
  \includegraphics[width=2.5in]{../Figures/11}\\
  \hspace{4 mm}  \\ 
  \includegraphics[width=.625\columnwidth]{../Figures/GBNGreps_w_1m_guideline}\\
  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.  The image with the three replicate fire patterns has a red line indicating a position approximately 1.0~m above the burner.  This height corresponds with the height of the top of the 350~$^\circ$C mark in the FDS image.}
  \label{FDS_FirePattern_comp}
\end{figure}
